### 2008-08-12 doc/glite_gateway/glite_gateway.tex
Added citations

%{\centering \textit{\large Paper subtitle}\large \par}

@@

The purpose of this document is to describe this gLite specific plugin of the ARCLIB (Hivatkozni: jövőbeli Deliverable) to present the related command line utilities built on top of these libraries. The gateway library together with the tools enables seemless interoparability with gLite computing elements. It is possible, that relevant sections of this document will be moved into ARC1 userguide and into ARCLIB technical documentation. Interoperability with gLite storage element is provided by an other set of ARC library. This data library provides native interfaces to GridFTP SRM which is the main bulding blocks of a gLite storage element. A storage interopability is out of scope of this library.

@@

The latter solution was preferred by ARC1 developers, the gLite gateway library module has been implemented in the ARCLIB and the gateway functionality will be transparently offered via the usual Nordugrid command line tools. An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}.\par

@@

\caption{\label{fig:Chart 1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library module based approach works. The user will be able to express his requirements in the job description document using any of the xRSL, JDL or JSDL languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client enables the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage element. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note, that not all the functionality described on the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!}}

@@

Nevertheless the KnowARC project chose the CREAM version 2\cite{cream} as the gLite computing element interface.\par ... Hivatkozás a cikkre, mint CREAM-re...

@@

The ARCLIB gLite plugin have only one dependency. GridFTP components of the Globus Toolkit are needed to enable data staging functionality to those CREAM2 computing elements which offer input and output sandbox over a GridFTP enabled storage. Unfortunately the gateway library only works together with a strongly patched Globus verion. The Nordugrid patched Globus can be dowloaded from the Nordugrid download area\footnote{\url{http://download.nordugrid.org/software/globus/}}. Further information about the Nordugrid Globus patches can be read on the Nordugrid page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. It is worth to mention that the user will need a VOMS proxy certificate in order to use the command line tools against a CREAM2 service. This VOMS proxy can be generated by using the VOMS client tools. It is only the VOMS enabled proxy certificate that is needed here, appart from this no VOMS component needed.\par
The ARC gLite gateway plugin library and the temporary command line utilities are incorporated into ARC1 releases. The source code is available from the ARC1 SVN repository\footnote{\url{http://svn.nordugrid.org/repos/nordugrid/arc1/}} and binary packages are provided at the Nordugrid download area. The build and installation instructions are given in the README file distributed together with the software. A step-by-step guide for Debian binary installation can be found in the appendix \ref{Debian install} Installation from Debian binary packages.

@@

... 1 bekezdés arról, hogy SOAP a hed(Hivatkozni!!!) SOAP framework-jét használja 'fully integrated'... az előző deliverable-ben a kommunikáció gsoap-ot használt, ez az egyik nagy előrelépés, hogy ezt lecseréltük...

@@

The well known ARC commands (ngsub, ngget, ... See: The Nordugrid/ARC User Guide\cite{userguide}!) will provide seemless access and integration with gLite computing elements. Full transparency will be achieved through the gLite gateway ARCLIB plugin. An ordinary user will use the same set of commands regardless of what type of CE to access. The user will be able to specify grid jobs described both in the gLite (JDL) and the Nordugrid (JSDL, XRSL) job description languages. ... +++Kipofozni. Hivatkozások... The client will perform automatic conversion between the different job description languages.\par
Unfortunately the interoperability features offered by the gLite gateway library are not yet integrated into the Nordugrid commands. Also the current version of ARCLIB does not offer the full spectrum of language transformations.

@@

... ldap parancs jön ide ...\par

@@

It is possible to express jobs in XRSL which have no equivalent in JDL. Speciﬁcally, in XRSL it is possible for input files downloaded from storage servers to have their names changed. This is not possible in JDL. So a user might in XRSL ask for this:

@@

That is not possible to express in JDL. It only allows the file to be downloaded as datafile1.txt. This could be solved by a wrapper script that renames files according to the XRSL speciﬁcation. This does not solve our problem completely however. For example if a user wants to concatenate the stdout from two jobs, he would write something like the following in XRSL:

>>>>

{\centering \textit{\large Technical description and user manual}\large \par}

@@

The purpose of this document is to describe this gLite\cite{glite} specific plugin of the ARCLIB (...Hivatkozni: jövőbeli Deliverable) to present the related command line utilities built on top of these libraries. The gateway library together with the tools enables seemless interoparability with gLite computing elements. It is possible, that relevant sections of this document will be moved into ARC1 userguide and into ARCLIB technical documentation. Interoperability with gLite storage element is provided by an other set of ARC library. This data library provides native interfaces to GridFTP\cite{gridftp} SRM which is the main bulding blocks of a gLite storage element. A storage interopability is out of scope of this library.

@@

The latter solution was preferred by ARC1 developers, the gLite gateway library module has been implemented in the ARCLIB and the gateway functionality will be transparently offered via the usual NorduGrid command line tools. An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}.\par

@@

\caption{\label{fig:Chart 1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library module based approach works. The user will be able to express his requirements in the job description document using any of the xRSL\cite{xrsl}, JDL or JSDL\cite{jsdl} languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client enables the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage element. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note, that not all the functionality described on the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!}}

@@

Nevertheless the KnowARC project chose the CREAM version 2\cite{cream} as the gLite computing element interface.\par

@@

The ARCLIB gLite plugin have only one dependency. GridFTP components of the Globus Toolkit\cite{globus} are needed to enable data staging functionality to those CREAM2 computing elements which offer input and output sandbox over a GridFTP enabled storage. Unfortunately the gateway library only works together with a strongly patched Globus verion. The NorduGrid patched Globus can be dowloaded from the NorduGrid download area\footnote{\url{http://download.nordugrid.org/software/globus/}}. Further information about the NorduGrid Globus patches can be read on the NorduGrid page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. It is worth to mention that the user will need a VOMS\cite{voms} proxy certificate in order to use the command line tools against a CREAM2 service. This VOMS proxy can be generated by using the VOMS client tools. It is only the VOMS enabled proxy certificate that is needed here, appart from this no VOMS component needed.\par
The ARC gLite gateway plugin library and the temporary command line utilities are incorporated into ARC1 releases. The source code is available from the ARC1 SVN repository\footnote{\url{http://svn.nordugrid.org/repos/nordugrid/arc1/}} and binary packages are provided at the NorduGrid download area. The build and installation instructions are given in the README file distributed together with the software. A step-by-step guide for Debian binary installation can be found in the appendix \ref{Debian install} Installation from Debian binary packages.

@@

... 1 bekezdés arról, hogy SOAP a hed(Hivatkozni!!!) SOAP framework-jét használja 'fully integrated'... az előző deliverable-ben a kommunikáció gSOAP-ot használt, ez az egyik nagy előrelépés, hogy ezt lecseréltük...\cite{gsoap}... 

@@

The well known ARC commands (ngsub, ngget, See: The NorduGrid/ARC User Guide\cite{userguide}!) will provide seemless access and integration with gLite computing elements. Full transparency will be achieved through the gLite gateway ARCLIB plugin. An ordinary user will use the same set of commands regardless of what type of CE to access. The user will be able to specify grid jobs described both in the gLite (JDL) and the NorduGrid (JSDL, xRSL) job description languages. The client will perform automatic conversion between the different job description languages.\par
Unfortunately the interoperability features offered by the gLite gateway library are not yet integrated into the NorduGrid commands. Also the current version of ARCLIB does not offer the full spectrum of language transformations.

@@

\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid \#\\*
\verb#        '(GlueCEUniqueID=*cream*)' | grep GlueCEInfoContactString | \#\\*
\verb#        awk '{print $2}' | sort | uniq#

@@

It is possible to express jobs in xRSL which have no equivalent in JDL. Speciﬁcally, in xRSL it is possible for input files downloaded from storage servers to have their names changed. This is not possible in JDL. So a user might in xRSL ask for this:

@@

That is not possible to express in JDL. It only allows the file to be downloaded as datafile1.txt. This could be solved by a wrapper script that renames files according to the xRSL speciﬁcation. This does not solve our problem completely however. For example if a user wants to concatenate the stdout from two jobs, he would write something like the following in xRSL:
